Stream of Consciousness Literature: A 'Joyceless' Linguistic Landscape

### 2024-04-25 paper/paper.qmd
final paper updates

However, this paper does recognize how reductive this quantification of language can be. When it comes to understand such social and human artifacts as language or literary texts, much is dependent on their context. As such, this paper will further discuss these weaknesses of the datasets under [Discussion].

@@

## Combined Bibliographies of Nine Selected Stream of Consciousness Texts

```{r}
#| echo: false
#| eval: true
#| label: tbl-combined
#| tbl-cap: "Sample Combined Bibliographies of 9 Selected Stream of Consciousness Texts"
#| warning: false

>>>>

However, this paper does recognize how reductive this quantification of language can be. When it comes to understand such social and human artifacts as language, much depends on their context. As such, this paper will further discuss these weaknesses of the datasets under [Discussion].

@@

## Combined Bibliographies from Five Authors

```{r}
#| echo: false
#| eval: true
#| label: tbl-combined
#| tbl-cap: "Sample Combined Bibliographies of Stream of Consciousness Texts from Five Authors"
#| warning: false
